A generalized definition of multidimensional item response theory parameters

### 2023-04-20 output/paper_draft/paper_M2PLM_parameters.Rmd
changes 1

Thus, inner product $`r LS_BASIS_INNER_PROD`$ has $`r INNER_PROD_MAT_EQ`$ as
Gram matrix, i.e., $`r INNER_PROD_EQ`$, with $`r INNER_PROD_MAT_ELEMENT_EQ`$ as
the $`r INNER_PROD_MATRIX_INDEX`$-th element of $`r INNER_PROD_MATRIX`$. As
$`r TRANSFORM_MATRIX`$ (and consequently $`r TRANSFORM_MATRIX_TRANSP`$) is
invertible, so $`r INNER_PROD_MATRIX`$ is, and $`r INNER_PROD_MATRIX_INV_EQ`$.

@@

@@

Since the response probability must be invariant, because of Equation
\@ref(eq:change-basis), parameter $`r DISCR_VECTOR`$ must also be transformed
in $`r DISCR_VECTOR_STD`$.
Equating the probabilities we get $a_1^{'}=P^{-1^T}a_i=M^{-1}Pa_i$ .
This shows that first a basis change to the standard base is performed and then
a transformation through $`r INNER_PROD_MATRIX_INV`$,
so the $`r DISCR_VECTOR_STD`$ are expressed in the standard basis.

>>>>

Thus, inner product $`r LS_BASIS_INNER_PROD`$ has $`r INNER_PROD_MAT_EQ`$ as
Gram matrix, i.e.$\langle \theta_j, \theta_k \rangle_B=\theta_j^{BT}M\theta_k^{B}$ with $`r INNER_PROD_MAT_ELEMENT_EQ`$ as
the $`r INNER_PROD_MATRIX_INDEX`$-th element of $`r INNER_PROD_MATRIX`$. As
$`r TRANSFORM_MATRIX`$ (and consequently $`r TRANSFORM_MATRIX_TRANSP`$) is
invertible, so $`r INNER_PROD_MATRIX`$ is, and $`r INNER_PROD_MATRIX_INV_EQ`$.

@@

BE CAREFUL with $e_k$

@@

Since the response probability must be invariant, because of Equation
\@ref(eq:change-basis), parameter $`r DISCR_VECTOR`$ must also be transformed
in $`r DISCR_VECTOR_STD`$.
Equating the probabilities we get $a_1^{'}=P^{-1^T}a_i$ .

JUSTIFY
